Quantifying and controlling biases in dark matter halo concentration estimates

### 2016-08-25 paper/ms.tex
all files updated

We impose two conditions on the approximate $\sigma_{\rm eff}^{2}$. It
must keep the dependence on $x$ that we have discovered for the
diagonal elements and must give similar curves of $\chi^{2}(c,x_i)$-$c$
around the minimum as the full covariance matrix.
We found that this effective $\sigma_{\rm eff}^2$ can be approximated
as

>>>>

We impose two conditions on the approximate $\sigma_{\rm eff}^{2}$. It
must keep the dependence on $x$ that we have discovered for the
diagonal elements and must give similar curves of $\chi^{2}(c,x_i)$
vs. $c$ around the minimum as the full covariance matrix.
We found that the effective $\sigma_{\rm eff}^2$ can be approximated
as
